\normalsize{A user-friendly tool to evaluate the effectiveness of no-take marine reserves}

### 2017-10-10 Manuscript.Rmd
Changed title

---
title: \normalsize{A general approach and tool to evaluate the effectiveness of no-take marine reserves}
header-includes:
- \usepackage{setspace}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
output:
  pdf_document:
    fig_caption: yes
fontsize: 12pt
bibliography:
- exported-references.bib
- packages.bib
csl: plos.csl
---

>>>>

---
title: \normalsize{A user-friendly tool to evaluate the effectiveness of no-take marine reserves}
header-includes:
- \usepackage{setspace}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
output:
  pdf_document:
    fig_caption: yes
fontsize: 12pt
bibliography:
- exported-references.bib
- packages.bib
csl: plos.csl
---
